Fig X

### 2020-03-09 analysis/figure-X.Rmd
extra figs

---
title: "Fig X"
author: "Rayna M Harris"
date: "2/20/2020"
output: html_document
---

@@

```{r}
candidategenes <- c("OXT", "AVP", "GNRH1",  "AR", "POMC", "AGRP",
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9")

@@

```{r vsd}
geneids <- read_csv("../metadata/00_geneinfo.csv")

@@

```{r}
makeboxplots <- function(df, whichgene, myylab, whichsex){
  p <- df %>%
    filter(treatment %in% charlevels,
           gene %in% whichgene,
           sex %in% whichsex) %>%
    filter(treatment != "control") %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot() + 
    #geom_point() +
    facet_wrap(~sex) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(y = myylab , x = "Parental stage", subtitle = "") +
    theme(axis.title.y = element_markdown())
  return(p)
}

@@

>>>>

---
title: "Fig X"
author: "Rayna M Harris"
date: "2/20/2020"
output: md_document
---

@@

```{r}
library(tidyverse)
library(ggtext)
library(cowplot)
library(ggpubr)

source("../R/themes.R")

knitr::opts_chunk$set(echo = TRUE, message = F, fig.path = "../figures/")

candidategenes <- c("OXT", "AVP", "GNRH1", "GNRHR", "CGNRH-R",
                    "AR", "POMC", "AGRP", 
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2","VIP",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2","GRIA1",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16", 
                    "DIO3", "DIO2", "DIO1")

@@

```{r }
geneids <- read_csv("../metadata/00_geneinfo.csv")

@@

```{r fig-x, fig.width=7, fig.height=5}
makeboxplots <- function(df, whichgene, myylab, whichsex){
  p <- df %>%
    filter(treatment %in% charlevels,
           gene %in% whichgene,
           sex %in% whichsex) %>%
    filter(treatment != "control") %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot() + 
    #geom_point() +
    facet_wrap(~sex) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(y = myylab , x = "Parental stage", subtitle = "") +
    theme(axis.title.y = element_markdown())
  return(p)
}

@@

plot_grid(p23, p56, p89, nrow = 3)

candidatevsd$tissue = factor(candidatevsd$tissue, levels = tissuelevel)

plotcandidategene <- function(whichgene, mysubtitle){
  p <- candidatevsd %>%
    filter(treatment %in% charlevels,
           gene %in% whichgene,
           sex %in% sexlevels) %>%
    filter(treatment != "control") %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot() + 
    #geom_point() +
    facet_wrap(~tissue, scales = "free_y") +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    theme(axis.title.y = element_markdown()) +
  labs(y = "variance-stabilized gene expression", x = "parental stage", 
       subtitle = mysubtitle)
  return(p)

}

a <- plotcandidategene("PRL", "PRL and ePRL expression") + 
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())
b <- plotcandidategene("VIP", "VIP expression") + theme(legend.position = "bottom") +
  guides(fill = FALSE)

plot_grid(a,b, nrow = 2, rel_heights = c(0.4,0.6))

ePRL <- candidatevsd  %>%
  filter(gene == "PRL") %>%
  mutate(bird = sapply(strsplit(samples, '\\_'), "[", 1)) %>%
  select(bird, sex, tissue, treatment, counts)  %>%
  pivot_wider(names_from = tissue, values_from = counts) 
ePRL

a <- ggplot(ePRL, aes( y = hypothalamus, x = pituitary)) +
  geom_point(aes(color = treatment)) +
  scale_color_manual(values = allcolors) +
  theme(legend.position = "none") +
  geom_smooth(method = "lm", aes(color = sex)) +
  labs(x = "pituitary PRL", y = "hypothalamic ePRL" )

b <- ggplot(ePRL, aes( y = gonad, x = pituitary)) +
  geom_point(aes(color = treatment)) +
  scale_color_manual(values = allcolors) +
  theme(legend.position = "none") +
  geom_smooth(method = "lm", aes(color = sex))  +
  labs(x = "pituitary PRL", y = "gonadal ePRL" )

plot_grid(a,b)
